Taking Linear Logic Apart

### 2018-04-26 doc/tlla2018/main.tex
Put proofs from CP back... because otherwise my HCP proof isnt complete

  Logical Rules.
  \begin{center} \cpInfTens   \cpInfParr  \end{center}\vspace*{0.5\baselineskip}
  \begin{center} \cpInfOne    \cpInfBot   \end{center}\vspace*{0.5\baselineskip}
  \begin{center} \cpInfPlus1  \cpInfPlus2 \end{center}\vspace*{0.5\baselineskip}
  \begin{center} \cpInfWith               \end{center}\vspace*{0.5\baselineskip}
  \begin{center} \cpInfNil    \cpInfTop   \end{center}\vspace*{0.5\baselineskip}
\end{definition}
\cp enjoys subject reduction, progress, and termination~\cite{wadler2012}.

@@

\begin{lemma}[Type preservation for \equiv]\label{lem:hcp-preservation-equiv}
  If $\tm{P}\equiv\tm{Q}$, then $\seq[P]{\mathcal{G}}$ iff $\seq[Q]{\mathcal G}$.
\end{lemma}
\begin{proof}
  By induction on the derivation of $\tm{P}\equiv\tm{Q}$.
\end{proof}

\begin{theorem}[Subject reduction]\label{thm:hcp-preservation}
  If $\seq[P]{\mathcal{G}}$ and $\reducesto{P}{Q}$, then $\seq[Q]{\mathcal G}$.
\end{theorem}
\begin{proof}
  By induction on the derivation of $\reducesto{P}{Q}$.
\end{proof}

>>>>

  Logical Rules.
  \begin{center} \cpInfTens   \cpInfParr  \end{center}\vspace*{0.5\baselineskip}
  \begin{center} \cpInfOne    \cpInfBot   \end{center}\vspace*{0.5\baselineskip}
  \begin{center} \cpInfPlus1  \cpInfPlus2 \end{center}\vspace*{0.5\baselineskip}
  \begin{center} \cpInfWith               \end{center}\vspace*{0.5\baselineskip}
  \begin{center} \cpInfNil    \cpInfTop   \end{center}\vspace*{0.5\baselineskip}
\end{definition}
\cp enjoys subject reduction, progress, and termination~\cite{wadler2012}.
\begin{lemma}[Preservation for $\equiv$]\label{lem:cp-preservation-equiv}
  If $\tm{P}\equiv\tm{Q}$, then $\seq[P]{\Gamma}$ iff $\seq[Q]{\Gamma}$.
\end{lemma}
\begin{proof}
  By induction on the derivation of $\tm{P}\equiv\tm{Q}$.
\end{proof}
\begin{theorem}[Preservation]\label{thm:cp-preservation}
  If $\seq[P]{\Gamma}$ and $\reducesto{P}{Q}$, then $\seq[Q]{\Gamma}$.
\end{theorem}
\begin{proof}
  By induction on the derivation of $\reducesto{P}{Q}$.
\end{proof}
\begin{theorem}[Progress]\label{thm:cp-progress}
  If $\seq[P]{\Gamma}$, then there exists a $\tm{Q}$ such that
  $\tm{P}\Longrightarrow^\star\tm{Q}$ and $\tm{Q}$ is not a cut.
\end{theorem}
\begin{proof}
  By induction on the derivation of $\seq[P]{\Gamma}$.
  If the last rule is \textsc{Cut}, there are four cases:
  \begin{enumerate*}[label={\alph*)}]
  \item
    if either side of the cut is an axiom, we apply \cpRedAxCut1;
  \item
    if either side of the cut is itself a cut, we recursively eliminate the cut;
  \item
    if both sides are logical rules acting on the cut formula, we apply
    one of the $\beta$-rules;
  \item
    otherwise, at least one side is a logical rule acting on a formula other
    than the cut formula, in which case we apply one of the $\kappa$-rules.
  \end{enumerate*}
\end{proof}

@@

\begin{lemma}[Preservation for $\equiv$]\label{lem:hcp-preservation-equiv}
  If $\tm{P}\equiv\tm{Q}$, then $\seq[P]{\mathcal{G}}$ iff $\seq[Q]{\mathcal G}$.
\end{lemma}
\begin{proof}
  By induction on the derivation of $\tm{P}\equiv\tm{Q}$.
\end{proof}

\begin{theorem}[Preservation]\label{thm:hcp-preservation}
  If $\seq[P]{\mathcal{G}}$ and $\reducesto{P}{Q}$, then $\seq[Q]{\mathcal G}$.
\end{theorem}
\begin{proof}
  By induction on the derivation of $\reducesto{P}{Q}$.
\end{proof}
